non_phylo_analyses

### 2018-04-09 reports/non_phylo_model.Rmd
adding some dredging and model-averaging potential code

>>>>

a model averaging approach
```{r}
#### Automated Approach ####
#### Computes all possible subsets of global model
df3 <- df2 %>%
  mutate(response = log(urban_median)) %>%
  mutate(body_size_logged = log(mean_body_size)) %>%
  mutate(clutch_size_logged = log(clutch_size))

glob.mod <- lm(response~body_size_logged + clutch_size_logged + feeding_habitat_generalism + brain_residual + Habitat_agricultural,
               data=df3, na.action = "na.fail", weights=(df3$N/df3$unique_localities))

library(arm)
stdz.model <- standardize(glob.mod)

model.set <- dredge(stdz.model)

model.set

#### selects all models with deltaAic < 4
top.models <- get.models(model.set, cumsum(weight) <= 0.95)

#### how many top models
length(top.models)

#### Ranks these models based on AICc
my.models <- model.sel(top.models, rank="AICc")

 #### Prints the top models (selected above)
print.data.frame(my.models, digits=2)

Averaged_models <- model.avg(top.models)

summary(Averaged_models)
confint(Averaged_models, full=TRUE)
```

Now repeat on the full model (will take a while so let it run overnight)
```{r}
df3 <- df2 %>%
  mutate(response = log(urban_median)) %>%
  mutate(body_size_logged = log(mean_body_size)) %>%
  mutate(clutch_size_logged = log(clutch_size))

glob.mod <- lm(response ~ body_size_logged + clutch_size_logged + feeding_habitat_generalism + brain_residual + Habitat_agricultural +
                 breeding_habitat_generalism + granivore + insectivore + carrion_eater + plant_eater + diet_generalism + movement_class +
                 groun_nesting + hollow_nesting + nest_generalism + breeding + nest_aggregation + feeding_aggregation + Habitat_grass_shrubland +
                 Habitat_tree_forest, data=df3, na.action = "na.fail", weights=(df3$N/df3$unique_localities))

library(arm)
stdz.model <- standardize(glob.mod)

model.set <- dredge(stdz.model, extra="R^2")

model.set

#### selects all models with deltaAic < 4
top.models <- get.models(model.set, cumsum(weight) <= 0.95)

#### how many top models
length(top.models)

#### Ranks these models based on AICc
my.models <- model.sel(top.models, rank="AICc")

 #### Prints the top models (selected above)
print.data.frame(my.models, digits=2)

Averaged_models <- model.avg(top.models)

summary(Averaged_models)
confint(Averaged_models, full=TRUE)
